Do We Judge Children's Books by Their Covers? 

### 2024-12-04 paper/paper.qmd
Slight improvement in wording

# Introduction {#sec-intro}
The rise of user-generated content has transformed how consumers interact with media, especially when it come to book ratings. These ratings serve as an indirect reflection of a book's quality and readers' perceptions, serving as one of the few pieces of information that help potential readers to form initial impressions. As they play a crucial role in guiding decisions, consequently, it has become standard practice to use book ratings as a predictor variable in recommendation systems, serving as a key indicator of how much a reader enjoys a book.

@@

## Ethical Considerations
As we are interviewing children, ensuring the ethical integrity of the survey is crucial.The following considerations are taken into account:

@@

A sample survey can be found at: [Link](https://docs.google.com/forms/d/e/1FAIpQLSeIMsn9aL4JJsZOZtFYFiE_HoZZbaU_g5v84bLXZpoZKjtNpQ/viewform?usp=sf_link). Thank @stantcheva2023surveys and @chen2018methods's paper in providing valuable guidance in creating survey.

>>>>

# Introduction {#sec-intro}
The rise of user-generated content has transformed how consumers interact with media, especially when it come to book ratings. These ratings serve as an indirect reflection of a book's quality and readers' perceptions, serving as one of the few pieces of information that help potential readers to form initial impressions. As they play a irreplaceable role in guiding decisions, consequently, it has become standard practice to use book ratings as a predictor variable in recommendation systems, serving as a key indicator of how much a reader enjoys a book.

@@

## Ethical Considerations
As we are interviewing children, we must ensure the ethical integrity of the survey. The following considerations are taken into account:

@@

A sample survey can be found at: [Link](https://docs.google.com/forms/d/e/1FAIpQLSeIMsn9aL4JJsZOZtFYFiE_HoZZbaU_g5v84bLXZpoZKjtNpQ/viewform?usp=sf_link). Thank @stantcheva2023surveys and @chen2018methods's paper in providing guidance in creating survey.
